Fast and adaptive cointegration based model for forecasting high frequency financial time series

### 2016-04-19 articles-conferences/iscef2016/src/background.tex
avance martes
fixing definition of a VECM model (ISCEF comment)

VECM is a special case of the VAR \cite{sims1980} model and both describe the joint behaviour
of a set of variables.

The VAR($p$) model is a general framework describing the behaviour of a
set of $l$ endogenous variables as a linear combination of their last $p$
values, where $l,p\in\mathbb{N}$. 
In our case, each one of these $l$ variables is a scalar time series
$y_{\lambda,t}$, $\lambda=1,\dots,l$, and we represent them all together
at time $t$ by the the vector time series:
\begin{equation}
\label{eq:variables}
\mathbf{y}_t = 
\begin{bmatrix} y_{1,t} & y_{2,t} & \dots & y_{l,t} \end{bmatrix}^\top.
\end{equation}
\noindent
Notice that the vectors $\mathbf{y}_t$ are assumed to be $l$-dimensional.

@@

%\subsection{Ordinary Least Squares method}
%
%The solution $\widehat{\mathbf{A}}$ to
%equation~(\ref{eq:vareq}) can be obtained by the ordinary least squares (OLS)
%method. $\widehat{\mathbf{X}}$ is the solution of the quadratic optimization problem
%\begin{equation*}
%\widehat{\mathbf{X}} = \underset{\mathbf{X}}{\text{Arg\;min}}
%\|\mathbf{A}\mathbf{X}-\mathbf{B}\|_2^2
%\end{equation*}
%\noindent for which the solution $\widehat{\mathbf{X}}$ is well-known:
%\begin{equation*}
%\label{eq:MP}
%\widehat{\mathbf{X}}=\mathbf{A}^{\!\!+}\,\mathbf{B}
%\end{equation*}
%\noindent where $\mathbf{A}^{\!\!+}$ is the Moore-Penrose pseudo-inverse
%which, when $\mathbf{A}$ is full rank, can be written as follows: 
%\begin{equation}
%\label{eq:pseudoinverse}
%\mathbf{A}^{\!\!+}= (\mathbf{A}^{\!\!\top} \mathbf{A})^{-1}\mathbf{A}^{\!\!\top} \, .
%\end{equation}
%when $\mathbf{A}$ is not full rank, i.e
%$rank(\mathbf{A})=k <  n \leq m$, $\mathbf{A}^\top \mathbf{A}$ is
%always singular and equation~(\ref{eq:pseudoinverse}) cannot be used.
%More generally, the pseudo-inverse is best computed using the compact
%singular value decomposition (SVD) of $\mathbf{A}$ which is:
%\begin{equation*}
%    \label{eq:compactsvd}
%    \mathbf{A}=
%    \mathbf{U_1}
%    \boldsymbol \Sigma_1
%    \mathbf{V}_1^{\top} \, .
%\end{equation*}
%Pseudo-inverse can then be written as follows:
%\begin{equation*}
%\label{eq:pseudoinversesvd}
%\mathbf{A}^{\!\!+} = \mathbf{V}_1 \boldsymbol \Sigma_1^{-1} \mathbf{U}_1^\top \, .
%\end{equation*}

>>>>

Vector error correction model (VECM) describe the joint behaviour
of a set of variables and can be derived from the simple Vector Autoregressive model (VAR) \cite{sims1980} model.
The VAR($p$) model is a framework describing the behaviour of a
set of $l$ endogenous and stationary variables as a linear combination of their last $p$
values, where $l,p\in\mathbb{N}$. 
In our case, each one of these $l$ variables is a scalar time series
$y_{\lambda,t}$, $\lambda=1,\dots,l$, and we represent them all together
at time $t$ by the the vector time series:
\begin{equation}
\label{eq:variables}
\mathbf{y}_t = 
\begin{bmatrix} y_{1,t} & y_{2,t} & \dots & y_{l,t} \end{bmatrix}^\top.
\end{equation}
\noindent
Notice that the vectors $\mathbf{y}_t$ are assumed to be $l$-dimensional.

@@
